SAT Competition 2020\tnoteref{title}

### 2021-01-03 paper/main.tex
main track plots

>>>>

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-SAT.pdf}
\caption{Performance of the top 10 solvers + VBS on Main track satisfiable benchmarks}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-UNSAT.pdf}
\caption{Performance of the top 10 solvers + VBS on Main track unsatisfiable benchmarks}
\end{figure}
